\documentclass[line, margin]{res}
\usepackage{enumitem}
\usepackage{multicol}
\linespread{.9}
\addtolength{\topmargin}{-.5in}

\begin{document}
\name{{\LARGE Drew Kowalik}}
\address{San Francisco Bay Area\\ (843) 696-9395\\ drew.kowalik@gmail.com}

\begin{resume}
\section{EDUCATION}
 Bachelor of Science in Business Administration\\
 University of South Carolina\\
 Major: Finance || Minor: Economics\\
 GPA: 3.9
 
\section{SKILLS}
\begin{multicols}{4}
\begin{itemize}[leftmargin=10pt]
\item Ruby
\item Ruby on Rails
\item JavaScript
\item jQuery
\item Backbone.js
\item RSpec
\item SQL
\item SalesForce.com
\item \LaTeX
\item AWS
\item Python
\item Git
\end{itemize}
\end{multicols}

\section{PROJECTS}
{\large Meme Generator} \hfill meme-generator.herokuapp.com
\begin{itemize}[leftmargin=10pt]
\item Github: github.com/infecto/meme-generator
\item Technology Stack: Backbone.js, HTML5, Rails RESTful API, Amazon S3, Heroku
\item Application generates meme via Canvas, uploads final image to Amazon S3.
\end{itemize}

{\large Asteroids} \hfill infecto.github.io/asteroids/
\begin{itemize}[leftmargin=10pt]
\item Github: github.com/infecto/asteroids
\item Technology Stack: JavaScript, HTML5 (Canvas)
\item Clone of Atari classic Asteroids.
\end{itemize}

\section{EXPERIENCE}
{\large VP of Informatics} \hfill 2012-2013\\
\textit{Equiscript}
\begin{itemize}[leftmargin=10pt]
\item Salesforce.com development: Architecture, Data Integrity, User Experience. 
\item Amazon Web Services infrastructure using EC2, EBS, S3 and RDS.
\item MSSQL Server: Architecture, Stored Procedures, Data Analytics.
\item Analyzed large datasets (1+ million records) from healthcare entities to identify key patient characteristics.
\end{itemize}

{\large Information Systems Manager} \hfill 2011-2012\\
\textit{Equiscript}
\begin{itemize}[leftmargin=10pt]
\item Month-end financial \& ad-hoc operational reporting.
\item Developed new revenue forecasting model that increased accuracy by 4.9\%.
\end{itemize}

{\large Market Analyst} \hfill 2010-2011\\
\textit{Cassatt Short Term Fund}
\begin{itemize}[leftmargin=10pt]
\item  Analyzed most statements filed with SEC for trade arbitrage.
\item Developed trading software that managed over \$2 million in average daily dollar volume.
\end{itemize}
 
{\large Associate Equity Research Analyst} \hfill 2008-2010\\
\textit{New Constructs}
\begin{itemize}[leftmargin=10pt]
\item Examined and gathered data from 10-K statements, including key data from the Management Discussion and Analysis and the Notes to the Financial Statements of 10-K filings.
\item Researched and implemented treatment methodologies for new accounting standards and line items.
\end{itemize}

\end{resume}
\end{document}